Bayesian phylogenetic estimation of fossil ages

### 2015-09-02 fossilDating.tex
changes Tanja

First we determined $p(t|M_\mathcal{T})$ for the prior distributions as in \autocite{gavr2014} ($T: Unif(0,160), d: lognorm(-3.5,1.5), r: Unif(0,1), s: Unif(0,1)$). This prior specification leads to a distribution of sampling time with almost all mass close to the present (xxx give precise values, Figure xxx, black line). 
Second we  determined $p(t|M_\mathcal{T})$ for the prior distributions ($T: Unif(0,160), d: lognorm(-3.5,0.5), r: Unif(0,1), s: Unif(0,1)$). This produces a prior where larger sampling times have a non-negligable weight (Figure xxx, red line).

blabla on only d affecting the prior  shape $p(t|M_\mathcal{T})$ really.

>>>>

First we determined $p(t|M_\mathcal{T})$ for the prior distributions as in \autocite{gavr2014} ($T: Unif(0,160), d: lognorm(-3.5,1.5), r: Unif(0,1), s: Unif(0,1)$). This prior specification leads to a distribution of sampling time with almost all mass close to the present (xxx give precise values, Figure xxx, black line).

Second we  determined $p(t|M_\mathcal{T})$ for the following prior distributions $d: lognorm(-3.5,0.5), r: Unif(0,1)$. For $s$ we assume an implicit prior: lognorm(-2,1) for $\psi$, and $s=\psi/(\mu+\psi)$. For $T$, we also assume an implicit prior. We assume a uniform distribution on $[1,100]$ for the number of present day species, $N$. In expectation, we have $N=  \frac{e^{d T}}{1-p_0(T)}$ species after time $T$. This leads to $T=\log((1-r)N +r)/d$.
This produces a prior where larger sampling times have a non-negligable weight (Figure xxx, red line).
The implicit prior on $s$ assures that we do not obtain huge sampling rates (which is the case if $s$ and $r$ close to $1$). The implicit prior on $T$ assures that we do not obtain trees with arbitrary large number of extant species (which is the case for large $T$ and large $d$).
